Paper figures

### 2019-05-19 voltagebudget/analysis/paper_figures_redraft.Rmd
Added figure redraft
Revise ratio, story, and analysis.

Simplify everything!

mean_summary <- function(x) {
   m <- mean(x)
   return(c(y=m))
}
sample_n_groups = function(tbl, size, replace = FALSE, weight = NULL) {
  # regroup when done
  grps = tbl %>% groups %>% lapply(as.character) %>% unlist
  # check length of groups non-zero
  keep = tbl %>% summarise() %>% ungroup() %>% sample_n(size, replace, weight)
  # keep only selected groups, regroup because joins change count.
  # regrouping may be unnecessary but joins do something funky to grouping variable
  tbl %>% right_join(keep, by=grps) %>% group_by_(.dots = grps)
}
```

@@

# Summarize over As 
fig1 %>% 
  group_by(As, freq) %>% 
  summarise(
    N = 0,
    delta_spikes = mean(delta_spikes), 
    V_b = mean(V_b), 
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    n_spikes_pop = mean(n_spikes), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop), 
    variances = mean(variances)) -> fig2

@@

# Budget intro

```{r, fig.width=1.5, fig.height=0.7}
t_on = 0.23852
t_off = t_on + 2e-3

v_min = -68e-3
v_max = -50e-3
box_buffer = .5e-3

fig0 %>% 
  filter(t > 0.1, t < 0.29) %>%
  # ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=vm*1e3)) +
  # geom_ribbon(fill="blue", alpha=0.5) +
  ggplot(aes(x=t, y=vm*1e3)) +
  geom_line(color="black", alpha=1, size=.2) +
  geom_hline(yintercept=v_max*1e3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=v_min*1e3, color="black", linetype="dotted", size=0.5) +
 geom_rect(
    aes(
      xmin=t_on, 
      xmax=t_off, 
      ymin=(v_min - box_buffer)*1e3, 
      ymax=(v_max + box_buffer)*1e3),  
    fill="grey", color=NA, alpha=0.01, size=.01) +
  labs(x="Time (s)", y=expression(V[m] (mvolt))) +
  scale_x_continuous(breaks=c(0, 0.1, 0.2, 0.3), limits = c(0.1, 0.3)) +
  theme_classic() -> p1

fig0 %>% 
  filter(t > t_on, t < t_off) %>%
  ggplot(aes(x=t, ymin=v_min*1e3, ymax=osc*1e3)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_ribbon(aes(x=t, ymin=osc*1e3, ymax=comp*1e3), fill="purple", alpha=0.5) +
  geom_hline(yintercept=-50e-3*1e3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=v_min*1e3, color="black", linetype="dotted", size=0.5) +
  geom_rect(
    aes(
      xmin=t_on, 
      xmax=t_off, 
      ymin=(v_min - box_buffer)*1e3, 
      ymax=(v_max + box_buffer)*1e3),  
    fill=NA, color="grey", alpha=0.01, size=.6) +
  labs(x="", y="") +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      # axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p2

plot_grid <- rbind(c(1 , 1, 1, 1,1, 1, 1, NA, 2, 2, 2))
grid.arrange(p1, p2, layout_matrix=plot_grid)
rm(p1, p2, plot_grid)

# fig0 %>% 
#   filter(t > 0.15, t < 0.35) %>%
#   ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
#   geom_ribbon(fill="red", alpha=0.5) +
#   geom_ribbon(aes(x=t, ymin=osc*1e3, ymax=comp*1e3), fill="purple", alpha=0.5) +
#   geom_hline(yintercept=-50e-3*1e3, color="black", linetype="dotted", size=0.5) +
#   geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
#   geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3*1e3, ymax=-50e-3*1e3),  fill=NA, color="black", alpha=0.01, size=.2) +
#   # geom_hline(yintercept=-70e-3, color="black", size=1.5) +
#   # geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), color="grey", alpha=0.5) +
#   # geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3), fill=NA, color="grey", alpha=0.1) +
#   labs(x="Time (s)", y="") +
#   theme_classic() -> p2
```

# Trade-off

```{r, fig.width=1.5, fig.height=1.9}
fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors_pop*1e3, color=V_osc/V_b)) +
  geom_point(size=0.05, alpha=1) + 
  labs(x=expression(V[o]/V[b]), y="Avg. error (ms)") +
  # lims(y=c(0, 10)) +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  scale_color_gradient(low="darkgrey", high="red") +
  theme_classic() +
  theme(
    legend.position="none") -> p1

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_b, y=(variances_pop/n_spikes_pop)*1e3, color=V_osc/V_b)) +
  geom_point(size=0.05, alpha=1) + 
  labs(x=expression(V[o]/V[b]), y="Pop. variance (ms)") +
  scale_color_gradient(low="darkgrey", high="red") +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  theme_classic() +
  theme(
    legend.position="none") -> p2

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=errors_pop*1e3, y=(variances_pop/n_spikes_pop)*1e3, color=V_osc/V_b)) +
  geom_point(size=0.2, alpha=.6) +
  scale_color_gradient(low="darkgrey", high="red", name=expression(V[o]/V[b])) +
  # scale_color_gradient(low="darkgrey", high="red", name="A (namp)") +
  # geom_smooth(color="red", method=lm, alpha=0.2, size=.15, se=FALSE, linetype='solid') +
  labs(x="Avg. error (ms)", y="Pop. variance (ms)") +
  theme_classic() +
  theme(
    legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

# plot_grid <- rbind(
#   c(NA, NA, NA, NA, 4, 4,   4),
#   c(NA, NA, NA, NA, 4, 4,   4),
#   c(1,  1,  1,  1, 2, 2,   2),
#   c(1,  1,  1,  1, 2, 2,   2),
#   c(1,  1,  1,  1, 3, 3,   3),
#   c(1,  1,  1,  1, 3, 3,   3))#,
  # c(1,  1,  1,  NA, NA, NA))

plot_grid <- rbind(
  c(NA),
  c(3, 3))

grid.arrange(p3, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid)
```

# V_o/V_c

```{r, fig.width=2.7, fig.height=2.2}

fig1 %>% 
  group_by(N) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors*1e3), 
            color="black", size=0.8) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1

fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_comp, y=(variances/n_spikes)*1e3, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=(variances_pop/n_spikes_pop)*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o]/V[c]), y="Variance (ms)") -> p2

# # Norm error here
# fig1 %>% 
# filter(V_osc/V_comp < 3) %>% 
#   filter(freq == 20) %>% 
#   group_by(N, freq) %>% 
#   mutate(norm_errors = errors/max(errors)) -> tmp1
# 
# tmp1 %>% 
#   group_by(As) %>% 
#   summarise(
#     N = 0,
#     norm_errors = mean(norm_errors),
#     V_b = mean(V_b), 
#     V_osc = mean(V_osc), 
#     V_comp = mean(V_comp)) -> tmp2
# 
# tmp1 %>% 
#   group_by(N) %>% 
#   filter(V_osc/V_comp <= 3) %>% 
#   filter(freq == 20) %>%
#   group_by(N) %>%
#   mutate(V_free_initial = round(max(V_free), 3)) %>%
#   filter(V_free_initial > 0) %>%
#   ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
#   geom_line(size=0.5, alpha=0.2, color="grey") + 
#   geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
#   geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
#   theme_classic() +
#   geom_line(data=tmp2, 
#             aes(x=V_osc/V_comp, y=norm_errors), 
#             color="black", size=0.8) +
#   labs(x=expression(V[o]/V[c]), y="Norm. error") -> p2

max_N <- max(fig1$N)

fig1 %>% 
  filter(freq==20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 24, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
  geom_line(size=.5, alpha=0.9, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  facet_wrap(~rank, nrow=3) +
  theme_classic() + 
  scale_x_continuous(breaks=c(0, 1, 2)) +
  scale_y_continuous(breaks=c(0, 10)) +
  theme(
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),s
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p3

plot_grid <- rbind(
  c(1, 1, 1, 2, 2), 
  c(1, 1, 1, 2, 2), 
  c(1, 1, 1, 2, 2),
  c(1, 1, 1, NA, NA),
  c(3, 3, 3, 3, 3),
  c(3, 3, 3, 3, 3),
  c(3, 3, 3, 3, 3))
  # c(3, 3, 3, 4, 4),
  # c(3, 3, 3, 4, 4),
  # c(3, 3, 3, 4, 4))
grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid, max_N)
```

$ V_o and variance

```{r, fig.width=2.8, fig.height=3.2}
max_N <- max(fig1$N)

fig1 %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, group=N, color=factor(delta_spikes))) +
  geom_line(size=0.4, alpha=0.6) + 
  scale_colour_brewer(
    palette = "Reds", guide=guide_legend(title="Spike\ncount", nrow=3)) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
  theme_classic() + theme(legend.position = c(1.25, -0.8), 
        legend.background = element_rect(colour ="black"),
        legend.key.size = unit(.5, "cm"),
        legend.title = element_text(size=10),
        legend.text = element_text(size=10)) -> p1

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(y=V_osc/V_comp, x=factor(delta_spikes), group=delta_spikes)) +
  geom_jitter(aes(color=factor(delta_spikes)), size=0.01, alpha=0.1, width=0.2) +
  geom_boxplot(outlier.colour = NA, alpha=0.9, width=0.2) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  geom_hline(yintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_hline(yintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  theme(legend.position = "none") +
  labs(y=expression(V[o]/V[c]), x="Spike count") + 
  coord_flip()  -> p2

# -
M = min(fig2$variances_pop/fig2$n_spikes_pop)
fig1 %>% 
  filter(freq==20) %>% 
  mutate(quantile = ntile(V_osc, 10)) %>%
  filter(quantile %in% c(1, 10)) %>% 
  ggplot(aes(x=(variances/n_spikes)*1e3, fill=factor(quantile), group=quantile)) +
  geom_density(alpha=0.6, size=0.2, color="black") +
  geom_vline(xintercept = M*1e3, color="black") +
  labs(x="Variance (ms)", y="Density (AU)") +
  scale_fill_manual(
    # values=c("#FFDED3", "#FD0D11"), 
    values=c("grey", "black"),
    name=expression("Deciles V"[o]), 
    labels=c("0 - 10%", "90 - 100%")) +
  theme_classic() +
  theme(
    legend.position="bottom", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8) ) -> p3

# fig1 %>% 
#   filter(freq == 20) %>% 
#   group_by(N) %>%
#   mutate(V_free_initial = round(max(V_free), 3)) %>%
#   filter(V_free_initial > 0) %>%
#   ggplot(aes(x=(variances/n_spikes)*1e3, fill=factor(delta_spikes))) +
#   geom_density(alpha=0.6, size=0, color="black") +
#   scale_fill_brewer(palette = "Reds", name="Spike\ncount") +
#   geom_vline(xintercept = M*1e3, color="black", linetype="dotted") +
#   labs(x="Variance (ms)", y="Density (AU)") +
#   theme_classic() + 
#   theme(legend.position = c(1.25, 1.55), 
#         legend.background = element_rect(colour ="black"),
#         legend.key.size = unit(.5, "cm"),
#         legend.title = element_text(size=10),
#         legend.text = element_text(size=10)) -> p3

fig1 %>%
  filter(freq==20) %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ungroup() %>% 
  group_by(N) %>% 
  sample_n_groups(8) %>% 
  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) +
  facet_wrap(~N, nrow=8) +
  # geom_line(aes(x=V_osc/V_b, y=(variances_pop/n_spikes_pop)*1e3),
  #           color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  scale_y_continuous(breaks=c(6, 12)) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none",
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p4

fig1 %>%
  filter(freq==20) %>%
  filter(V_osc/V_comp <= 3) %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  sample_n_groups(8) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) +
  facet_wrap(~N, nrow=8) +
  # geom_line(aes(x=V_osc/V_b, y=errors_pop*1e3),
  #           color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  scale_x_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks=c(2, 8)) +
  labs(x=expression(V[o]/V[b]), y="Error (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none",
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p5

# Shift-add cartoon
t_start <- 0.2
t_stop <- 0.3

fig6 %>% 
  filter(t > t_start, t < t_stop) %>%
  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.3) +
  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.6) +
  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.6) +
  labs(x="", y="") +
  theme_classic() +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      # axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p6

fig7 %>% 
  filter(t > t_start, t < t_stop) %>%
  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.3) +
  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.6) +
  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.6) +
  labs(x="", y="") +
  theme_classic() +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      # axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p7

plot_grid <- rbind(
  c(1, 1, 1, NA, 4, 4, 5, 5),
  c(1, 1, 1, NA, 4, 4, 5, 5),
  c(1, 1, 1, NA, 4, 4, 5, 5),
  c(2, 2, 2, NA, 4, 4, 5, 5),
  c(2, 2, 2, NA, 4, 4, 5, 5),
  c(2, 2, 2, NA, 4, 4, 5, 5),
  c(3, 3, 3, NA, 4, 4, 5, 5),
  c(3, 3, 3, NA, NA, NA, NA, NA),
  c(3, 3, 3, NA, 6, 6, 7, 7),
  c(NA, NA, NA, NA, 6, 6, 7, 7))

  # c(3, 3, 3, NA, 4, 4, 5, 5))
  # c(3, 3, 3, NA, NA, NA, NA, NA))
  # c(3, 3, 3, NA, NA, NA, NA, NA))

grid.arrange(p1, p2, p3, p4, p5, p6, p7, layout_matrix=plot_grid)
rm(p1, p2, p3, p4, plot_grid, max_N, M)
```

# Control exps
## Freqs, noise, weight

```{r, fig.width=2.1, fig.height=2.4}
# --------------------------------------------------------------
# Freq
fig2 %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  group_by(N, freq) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = (variances_pop/n_spikes_pop)/max((variances_pop/n_spikes_pop))) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  labs(x=expression(V[o]/V[c]), y="Norm. error") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  group_by(N, freq) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = (variances_pop/n_spikes_pop)/max((variances_pop/n_spikes_pop))) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[c]), y="Norm. variance") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
  theme_classic() +
  # lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p2

# --------------------------------------------------------------
# Noise
fig9 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, sigma) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=10e-3*(sigma/10e-9) * 1e3/2, group=interaction(N, sigma))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[c]), y="Norm. error") +
  scale_color_gradient(low="grey", high="orange") +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

fig9 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, sigma) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = (variances_pop/n_spikes_pop)/max((variances_pop/n_spikes_pop))) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=10e-3*(sigma/10e-9) * 1e3 /2, group=interaction(N, sigma))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[c]), y="Norm. variance") +
  scale_color_gradient(low="grey", high="orange", name="Noise (mV)") +
  theme_classic() +
  # lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p4

# --------------------------------------------------------------
# Weight
fig11 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, weight) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=weight*1e9, group=interaction(N, weight))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[c]), y="Norm. error") +
  scale_color_gradient2(
    low="cornflowerblue", high="darkblue", mid="grey", midpoint=8.25e-09*1e9) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p5

>>>>

mean_summary <- function(x) {
   m <- mean(x)
   return(c(y=m))
}
sample_n_groups = function(tbl, size, replace = FALSE, weight = NULL) {
  # regroup when done
  grps = tbl %>% groups %>% lapply(as.character) %>% unlist
  # check length of groups non-zero
  keep = tbl %>% summarise() %>% ungroup() %>% sample_n(size, replace, weight)
  # keep only selected groups, regroup because joins change count.
  # regrouping may be unnecessary but joins do something funky to grouping variable
  tbl %>% right_join(keep, by=grps) %>% group_by_(.dots = grps)
}

ms <- 1000
mV <- 1000
```

@@

# Summarize over As 
fig1 %>% 
  group_by(N, freq) %>% 
  mutate(errors=normalize(errors),
            variances=normalize(variances)) -> fig1

fig1 %>% 
  group_by(As, freq) %>% 
  summarise(
    N = 0,
    delta_spikes = mean(delta_spikes), 
    V_b = mean(V_b), 
    V_osc = mean(V_osc), 
    V_free = mean(V_free), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    n_spikes_pop = mean(n_spikes), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop), 
    variances = mean(variances)) -> fig2

@@

# The trade off

```{r, fig.width=1.7, fig.height=2.8}
# Var
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc*mV, variances_pop*ms, group=freq)) +
  geom_point(size=.2, alpha=0.5) +
  xlab(expression(paste(V[o], " (mV)"))) +
  ylab("Variance (ms)") +
  theme_classic() -> p1
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc/V_comp, variances_pop*ms, group=freq)) +
  geom_point(size=.2, alpha=0.5) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="dashed") +
  xlab(expression(V[o]/V[c])) +
  ylab("Variance (ms)") +
  theme_classic() -> p2

# Error
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc*mV, errors_pop*ms, group=freq)) +
  geom_point(size=.2, alpha=0.5) +
  xlab(expression(paste(V[o], " (mV)"))) +
  ylab("Error (ms)") +
  theme_classic() -> p3
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc/V_comp, errors_pop*ms, group=freq)) +
  geom_point(size=.2, alpha=0.5) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="dashed") +
  xlab(expression(V[o]/V[c])) +
  ylab("Error (ms)") +
  theme_classic() -> p4

tmp <- fig2
tmp$state <- rep("pathological", nrow(tmp))
m <- tmp$V_osc/tmp$V_comp < 0.27
tmp$state[m] <- "healthy"

tmp %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=variances_pop*ms, errors_pop*ms, group=freq, color=state)) +
  geom_point(size=.2, alpha=0.9) +
  xlab("Variance (ms)") +
  ylab("Error (ms)") +
  scale_color_manual("", values=c("darkslategray3", "darkslategray")) +
  theme_classic() -> p5

plot_grid <- rbind(
  c(NA, NA, NA, NA),
  c(1, 1, 3, 3), 
  c(1, 1, 3, 3),
  c(1, 1, 3, 3),
  c(1, 1, 3, 3),
  c(NA, NA, NA, NA),
  c(2, 2, 4, 4),
  c(2, 2, 4, 4),
  c(2, 2, 4, 4),
  c(2, 2, 4, 4),
  c(NA, NA, NA, NA),
  c(5, 5, 5, 5),
  c(5, 5, 5, 5),
  c(5, 5, 5, 5),
  c(5, 5, 5, 5),
  c(5, 5, 5, 5),
  c(5, 5, 5, 5))

grid.arrange(p1, p2, p3, p4, p5, layout_matrix=plot_grid)
```

By looking at the ratio we identified a narrow region (V_o/V_c ~< 0.27) where the trade-off is approx linear across freq, and that accounts for approx. half the total change in both variance and error. We hypothesize that this narrow region can be considered a healthy range for modulation as it is maximially sensitive and linear -- representing the best possible trade-off irregardless of freq.

Sync efficiency is strongly dependent on other osc input. Strong synapses need strong oscillations. Weak synapses need weak oscillations. To stay in healthy range, oscillation strength should be tuned on a compartment basis, either dendritically or somatically or both.

# Vc and sync

```{r, fig.width=1.4, fig.height=1}
fig2 %>% 
  # filter(V_osc/V_comp <= ) %>%
  ggplot(aes(x=V_comp*mV, variances_pop*ms, color=V_osc*mV)) +
  geom_point(size=.2, alpha=0.5) +
  xlab(expression(paste(V[c], " (mV)"))) +
  ylab("Variance (ms)") +
  scale_color_gradient(expression(paste(V[o], " (mV)")), low="goldenrod1", high="firebrick3") +
  theme_classic() +
  theme(legend.key.width=unit(0.3,"cm"),
        legend.title=element_text(size=8),
        legend.text=element_text(size=8))
```

While the ratio determines the overall trade-off (above), again we see that about half the sync effect comes from weak oscillations (< 1 mV, orange) applied to strong inputs (i.e., V_c > 6 mV). However this story is complicated by the fact that the weaker Vc, the more sync is possible--though this sync is very high error.

# Freq. dependence

```{r, fig.width=1, fig.height=6}
fig2 %>% 
  filter(V_osc/V_comp <= 0.8) %>%
  ggplot(aes(x=V_osc/V_comp, y=variances_pop*ms)) +
  geom_point(size=.2, alpha=0.5) +
  facet_grid(freq~.) +
  xlab(expression(V[o]/V[c])) +
  ylab("Variance (ms)") +
  # geom_rect(
  #   mapping=aes(xmin=0.15, xmax=0.4, ymin=min(variances_pop*ms), ymax=max(variances_pop*ms)),
  #   color="darkslategray4", fill="darkslategray4", alpha=0.02) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="dashed") +
  theme_classic() +
  theme(strip.text.y = element_text(angle=0), strip.background = element_blank())
```

Fo far we've focused on error-variance relationships common between frequencies. There are also clearly frequency dependent effects

...

Faster oscillations offer less sync overall, and therefore have a more limited var-error range than slower oscillations. If we use the curveture of the variance curve to fine tune the healthy ratio / frequency, we see that...

TODO: get max second deriv. Use that to find the change point?

# Controls - Ws, noise, cell type
TODO

# Optimal derivation
```{r, fig.width=1.3, fig.height=2}
min_t <- min(fig4$ts)
